General constraints on magic distillation protocols from statistical mechanics

### 2021-05-25 magic_paper.tex
Appendix full clean-up. Comments in red to be accepted

\begin{figure}[t]
    \centering
        \includegraphics[scale=0.4]{figs/protocol_diagram.pdf}
    \caption{\textbf{Analysing magic protocols relative to a stabilizer reference state.} 
	A magic protocol aims to turn $n$ copies of some magic state $\rho$ to $m$ copies of some other state $\rho'$.
	Constraints on the efficiency of the protocol can be imposed by considering its action on a separate probe state $\tau$.
    } \ddd{[Not the clearest - we can zoom-chat on this.]}
    \label{fig:sketch}
\end{figure}

@@

We wish to consider how physical constraints that may be hardware specific, affect magic distillation rates. These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting. For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}. \nick{repeats intro}

@@

It is now possible to consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within. Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory. For example, how does temperature affect distillation bounds? Do isotropic maps have better bounds, or does bias towards some pure stabilizer state provide more freedom?
\nick{re-write based on new relative majorisation approach}

@@

As shown in Appendix \ref{lemma:Lorenz_linearity}, the Lorenz curve for any quasi-probability distribution obeys the following linearity condition
\begin{equation}
L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bx,
\end{equation}
for all $a >0$ and any $b \in \mathbb{R}$. We now have that
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } (\w_\epsilon , \r) \succ (\w_\epsilon', \r'),
\end{equation}
and also $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x$. However, using the above linearity property of the Lorenz curves we have that
\begin{align}
L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
&\mbox{ if and only if }& \nonumber \\
\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
\end{align}
The $(1-\epsilon)$ terms cancel on both sides and we get the required relative majorization conditions for the quasi-distributions in terms of their Lorenz curves.

@@

This in turn can be expressed in terms of Lorenz curves. To simplify notation, we denote by $L_{\rho | \sigma}(x)$ the Lorenz curve $L_{W_{\rho} | W_{\sigma}} (x)$. We therefore have that
\begin{equation}
\rho_1 \rightarrow \rho_2 \mbox{ within }\R_\sigma \mbox{ implies } L_{\rho_1 |\sigma} (x) \ge L_{\rho_2 |\sigma} (x),
\end{equation}
for all $x \in [0,1]$. Therefore, the magic state Lorenz curve condition can be used to impose upper bounds on magic distillation rates. Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints. Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to exponentially many constraints, of which though there are at most as many independent constraints as there are elbows in the Lorenz curve of the output state, as proved in~\cref{thm:elbows} of~\cref{app:frag}.
In principle, any one location $x$ provides some valid constraint leading to an upper distillation bound, while optimising over the location provides the strictest majorisation bound.

@@

\begin{proposition}\label{prop:rmajor}
Given probability distributions $\bmx, \bmy$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
  \begin{enumerate}
    \item[(i)] $\bmy = A\bmx$ and $\r' = A\r$ for a stochastic map $A$;
    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r'_i t}$ for all $t \in \mathbb{R}$;
    \item[(iii)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r'}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r'}(1)$.
  \end{enumerate}
\end{proposition}
The proofs for these can be found in~\cite{cit:marshall,ruch_mixing_1978,Renes_2016,Buscemi_2017} and references therein.

\begin{lemma}\label{L-concave} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. Then $L_{\p|\r}(x)$ is a concave function on $[0,1]$.
\begin{proof}Let $L_{\p|\r}(x)$ attain its maximum at $x=x_\star$. Then from the definition, the function is continuous, monotone increasing on $[0,x_\star]$, and monotone decreasing on $[x_\star, 1]$. Consider $a,b \in [0,1]$ with $a <b$ and some probability $q \in [0,1]$. If $a$ and $b$ both lie in either the interval $[0,x_\star]$ or $[x_\star, 1]$ then concavity follows immediately. Otherwise, $a$ is in the first interval and $b$ in the second interval. If $w=qa + (1-q)b$ lies in the first interval then
\begin{align}
qL_{\p|\r}(a) + (1-q)L_{\p|\r}(b) &\le qL_{\p|\r}(a) + (1-q)L_{\p|\r}(x_\star)\nonumber\\
& \le L_{\p|\r}(w)
\end{align}
\nick{second inequality isn't clear to me}
from monotonicity on the first interval. Otherwise, $w$ lies in the second interval and
\begin{align}
qL_{\p|\r}(a) + (1-q)L_{\p|\r}(b) &\le qL_{\p|\r}(x_\star) + (1-q)L_{\p|\r}(b)\nonumber\\
& \le L_{\p|\r}(w)
\end{align}
\nick{again second inequality isn't clear to me}
which follows from monotonicity on the second interval. Therefore the Lorenz curve is concave on $[0,1]$.
\end{proof}
\end{lemma}

The following result is used in the text to relate relative majorization of quasi-distributions to their Lorenz curves.
\begin{proposition}\label{lemma:Lorenz_linearity}
	Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. Let $a > 0$ and $b \in \mathbb{R}$ then $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$.
\end{proposition}
\begin{proof} 
	The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order. Since $a > 0$, the permutation $\pi$ puts  $(p_i/r_i)$ in non-increasing order too. We thus have
\begin{align*}
&\left( \sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)} \right) = \\ 
&\left( \sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)} \right) \nonumber,
\end{align*}
so the value of the Lorenz curve at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
\begin{align}
&L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b L_{\r|\r}(x_k) = \nonumber\\
&a L_{\p|\r} (x_k) + b x_k,
\end{align}
so we have $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any $x \in [0,1]$ due to linearity.
\end{proof}

@@

The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
\begin{proposition}
	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
\begin{equation}
W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) =W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)
\end{equation}
\end{proposition}
\begin{proof} This follows from the multiplicativity of the Wigner distribution. 
\begin{align}
W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) &= \frac{W_{\rho_A \otimes \rho_B} (\x_A \oplus \x_B)}{W_{\tau_A \otimes \tau_B} (\x_A \oplus \x_B)}\nonumber \\
 &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)\nonumber,
\end{align}
as claimed.
\end{proof}

%\subsection{Component-multiplicity pairs}
%\label{app:cmpairs}

In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.

@@

This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
\begin{lemma}
Consider two Wigner distributions $\W{\rho_A}, \W{\rho_B}$ with component-multiplicity pairs 
\begin{equation}
	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
\end{equation}
respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}$.
\end{lemma}
\begin{proof}
	This result is true because all components of $\W{\rho_A \otimes \rho_B}$ are of the form $w_i w_j'$ and 
\begin{equation*}
	\sum_{i}\sum_{j} m_i m_j' = \sum_{i} m_i \sum_{j} m_j' = d_A^2 d_B^2,
\end{equation*}
where $d_A, d_B$ are the dimensions of $\rho_A, \rho_B$ respectively, and
so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}$.
\end{proof}

In the case of distillation protocols, we are interested in $n$--copies of a single Wigner distribution. For this, we have the following result, which follows from combinatorics.

\begin{lemma}\label{lem:ncopycomponents}
	Suppose $W_\rho(\x)$ has $D$ component-multiplicity pairs $\{(w_i, m_i)\}$. Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, where $\q$ runs through all $K$-component vectors with non-negative integer components that sum to $n$, and
\begin{align}
W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}, \label{eq:M}
\end{align}
where the term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient.
\end{lemma}
\begin{proof}
	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
	\begin{equation*}
	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
	\end{equation*}

	We proceed by induction.	
	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
	The set $C_D^1$ consists of all vectors of this form, i.e. 
\begin{equation*}
	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
\end{equation*}
	It is also true by direct calculation that
\begin{equation*}
	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
\end{equation*}
Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W$.

	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W^{\otimes n}$.
	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
\begin{equation}
	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
\end{equation}

	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
\begin{align*}
	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
\end{align*}
where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
\begin{align*}
	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
\end{align*}
We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.

We have achieved a regrouping of the distribution components.
Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
\begin{align*}
	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
\end{align*}
which is the dimension of $W^{\otimes (n+1)}$.

Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W^{\otimes n}$, completing the proof.
\end{proof}

The rescaled distribution is also multiplicative, so a set of component-multiplicity pairs can be obtained for the $n$-copy rescaled distribution in the same fashion as for usual Wigner distributions.

We now prove the following result on the relation between majorization in a particular fragment and mana, which was stated in~\cref{sec:monotones_frag}.

\begingroup
\def\thetheorem{\ref{lem:lcmax}}
\begin{theorem}
	Given a magic state $\rho$, the maximum value $L_\star$ attained by the Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$. Moreover, the relative majorization constraint is stronger than mana in every fragment.
\end{theorem}
\addtocounter{theorem}{-1}
\endgroup
\begin{proof}
	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\x)$.
	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$ and so the components are sorted in non-increasing order.

>>>>

\begin{figure}[t]
    \centering
        \includegraphics[scale=0.4]{figs/protocol_diagram.pdf}
    \caption{\textbf{Analysing magic protocols relative to a stabilizer reference state.} 
	A magic protocol aims to turn $n$ copies of some magic state $\rho$ to $m$ copies of some other state $\rho'$.
	Constraints on the efficiency of the protocol can be imposed by considering its action on a separate probe state $\tau$ which tranforms to $\tau'$ with free energy $F \rightarrow F'$.
	A ``magic free energy'' $\phi \rightarrow \phi'$ connects the two state conversions under the protocol. \nick{FIX}
    }
    \label{fig:sketch}
\end{figure}

@@

\nick{repeats intro}
We wish to consider how physical constraints that may be hardware specific, affect magic distillation rates. These are not a priori encoded in the formulation of the magic theory, and constitute additional physical conditions on top of the underlying resource-theoretic accounting. For example, there may be non-trivial thermal noise in the physical set-up or the accessible operations, there might be strong bias in the noise present, or we might be limited in how easily certain gates can be realised.~\cite{Aliferis_2008, Stephens_2013, Li_2015, Babbush_2018, Tuckett_2019, Guillaud_2019, Fowler_2019}.

@@

\nick{re-write based on new relative majorisation approach}
It is now possible to consider magic distillation rates within $\sigma$--fragments and then see how the bounds on the distillation rates depend on the choice of the fragment we work within. Therefore, this route can potentially shed light on how the physics of a protocol constrain distillation rates above and beyond global constraints from the parent resource theory. For example, how does temperature affect distillation bounds? Do isotropic maps have better bounds, or does bias towards some pure stabilizer state provide more freedom?

@@

As shown in~\cref{lemma:Lorenz_linearity}, the Lorenz curve for any quasi-probability distribution obeys the following linearity condition
\begin{equation}
L_{a \w + b \r | \r} (x) = a L_{\w|\r} (x) + bx,
\end{equation}
for any $a >0$ and $b \in \mathbb{R}$. We now have that
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } (\w_\epsilon , \r) \succ (\w_\epsilon', \r'),
\end{equation}
and also $(\w_\epsilon , \r) \succ (\w_\epsilon', \r')$ if and only if $L_{\w_\epsilon |\r} (x) \ge L_{\w'_\epsilon |\r'} (x)$ for all $x$. However, using the above linearity property of the Lorenz curves we have that
\begin{align}
L_{\w_\epsilon |\r} (x) &\ge L_{\w'_\epsilon |\r'} (x) \nonumber \\ 
&\mbox{ if and only if }& \nonumber \\
\epsilon L_{\w |\r} (x) + (1-\epsilon) x &\ge \epsilon L_{\w' |\r'} (x) + (1-\epsilon) x.
\end{align}
The $(1-\epsilon)$ terms cancel on both sides and we get the required relative majorization conditions for the quasi-distributions in terms of their Lorenz curves.

@@

This in turn can be expressed in terms of Lorenz curves. To simplify notation, we denote by $L_{\rho | \sigma}(x)$ the Lorenz curve $L_{W_{\rho} | W_{\sigma}} (x)$. We therefore have that
\begin{equation}
\rho_1 \rightarrow \rho_2 \mbox{ within }\R_\sigma \mbox{ implies } L_{\rho_1 |\sigma} (x) \ge L_{\rho_2 |\sigma} (x),
\end{equation}
for all $x \in [0,1]$. Therefore, the magic state Lorenz curve condition can be used to impose upper bounds on magic distillation rates. Note, however, that unlike any monotone, this is not a single numerical constraint, but a \emph{family} of constraints. Indeed, for $n$ copies of a $d$--dimensional system the number of terms in $W_{\rho}$ is $d^{2n}$, so the Lorenz curve condition corresponds to exponentially many constraints, of which though there are at most as many independent constraints as there are elbows in the Lorenz curve of the output state, as proved in~\cref{thm:elbows}.
In principle, any one location $x$ provides some valid constraint leading to an upper distillation bound, while optimising over the location provides the strictest majorisation bound.

@@

\begin{proposition}\label{prop:rmajor}
Given probability distributions $\p, \q$, $\r , \r'$, such that the components of $\r$ and $\r'$ are positive, the following statements are equivalent:
  \begin{enumerate}
    \item[(i)] $\q = A\p$ and $\r' = A\r$ for a stochastic map $A$;
    \item[(ii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{p_i - r_i t} \leq \sum\limits_{i=1}^n \abs{q_i - r'_i t}$ for all $t \in \mathbb{R}$;
    \item[(iii)] $L_{\p|\r}(t) \leq L_{\q|\r'}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\p|\r}(1) = L_{\q|\r'}(1)$.
  \end{enumerate}
\end{proposition}
The proofs for these can be found in~\cite{cit:marshall,ruch_mixing_1978,Renes_2016,Buscemi_2017} and references therein.

\subsection{Relative majorization for quasi-distributions}
\label{app:rel_quasi}

We now show that the Lorenz curve is concave in the context of quasi-distributions.
\begin{lemma}\label{L-concave} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. Then $L_{\p|\r}(x)$ is a concave function on $[0,1]$.
\nick{
\begin{proof}
	The Lorenz curve of $\p$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k p_{\pi(i)})$ where $\pi$ is the permutation that puts $p_i/r_i$ in non-increasing order.
	By construction, the slope of the curve attains the values $p_{\pi(i)}/r_{\pi(i)}$ throughout the interval $[0,1]$, which is a non-increasing sequence due to the definition of $\pi$.
	Therefore, the Lorenz curve is concave.
\end{proof}
}
\begin{proof}Let $L_{\p|\r}(x)$ attain its maximum at $x=x_\star$. Then from the definition, the function is continuous, monotone increasing on $[0,x_\star]$, and monotone decreasing on $[x_\star, 1]$. Consider $a,b \in [0,1]$ with $a <b$ and some probability $q \in [0,1]$. If $a$ and $b$ both lie in either the interval $[0,x_\star]$ or $[x_\star, 1]$ then concavity follows immediately. Otherwise, $a$ is in the first interval and $b$ in the second interval. If $w=qa + (1-q)b$ lies in the first interval then
\begin{align}
qL_{\p|\r}(a) + (1-q)L_{\p|\r}(b) &\le qL_{\p|\r}(a) + (1-q)L_{\p|\r}(x_\star)\nonumber\\
& \le L_{\p|\r}(w)
\end{align}
\nick{second inequality isn't clear to me}
from monotonicity on the first interval. Otherwise, $w$ lies in the second interval and
\begin{align}
qL_{\p|\r}(a) + (1-q)L_{\p|\r}(b) &\le qL_{\p|\r}(x_\star) + (1-q)L_{\p|\r}(b)\nonumber\\
& \le L_{\p|\r}(w)
\end{align}
\nick{again second inequality isn't clear to me}
which follows from monotonicity on the second interval. Therefore the Lorenz curve is concave on $[0,1]$.
\end{proof}
\end{lemma}

The following result is used in~\cref{sec:lc} to prove that the Lorenz curve condition due to relative majorization is true for quasi-distributions.
\begin{proposition}\label{lemma:Lorenz_linearity}
	Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. 
	Then, $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$ for any constants $a > 0$ and $b \in \mathbb{R}$.
\end{proposition}
\begin{proof} 
	The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order. Since $a > 0$, the permutation $\pi$ puts  $(p_i/r_i)$ in non-increasing order too. We thus have
\begin{align*}
&\left( \sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)} \right) = \\ 
&\left( \sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)} \right) \nonumber,
\end{align*}
so the value of the Lorenz curve at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
\begin{align}
&L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b L_{\r|\r}(x_k) = \nonumber\\
&a L_{\p|\r} (x_k) + b x_k,
\end{align}
so we have $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any $x \in [0,1]$ due to linearity.
\end{proof}

@@

The following lemma shows that the re-scaled Lorenz curves behave in a natural way under tensor products. 
\begin{proposition}\label{prop:rescaled_multi}
	Let $\tau_A, \tau_B$ be full rank stabilizer states on systems $A$ and $B$, and let $\rho_A, \rho_B$ be arbitrary states on $A,B$. Then the rescaled quasi-distribution obeys
\begin{equation}
W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) =W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B)
\end{equation}
\end{proposition}
\begin{proof} This follows from the multiplicativity of the Wigner distribution,
\begin{align}
W_{\rho_A \otimes \rho_B | \tau_A \otimes \tau_B}(\bmx_A \oplus \bmx_B) &= \frac{W_{\rho_A \otimes \rho_B} (\x_A \oplus \x_B)}{W_{\tau_A \otimes \tau_B} (\x_A \oplus \x_B)}\nonumber \\
 &= \frac{W_{\rho_A } (\x_A )W_{\rho_B } (\x_B )}{W_{\tau_A } (\x_A )W_{\tau_B } (\x_B )}\nonumber \\
  &= W_{\rho_A | \tau_A}(\x_A) W_{\rho_B | \tau_B}(\x_B). \nonumber
\end{align}
\end{proof}

\subsection{Component-multiplicity pairs}
\label{app:cmpairs}

In general, a $1$--copy $d$--dimensional state $\rho$ is described by its $d^2$--dimensional Wigner distribution $\W{\rho}(\bmx)$. 
The distribution $\W{\rho}(\bmx)$ is defined on the phase space, but it can be convenient to re-express this using vector notation.
We discuss this in terms of Wigner distributions, but there is nothing to prevent the discussion from applying to rescaled Wigner distributions as well.

@@

This representation is more compact when a Wigner distribution has a lot of multiplicities, and allows for simple handling of multiple copies via the following fact.
\begin{lemma}
Consider two Wigner distributions $\W{\rho_A}(\x_A), \W{\rho_B}(\x_B)$ with component-multiplicity pairs 
\begin{equation}
	\{(w_i, m_i)\} \text{ and } \{(w_j', m_j')\},
\end{equation}
respectively. Then, $\{(w_i w_j', m_i m_j')\}$ gives component-multiplicity pairs for $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$.
\end{lemma}
\begin{proof}
	This result is true because all components of $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$ are of the form $w_i w_j'$ and 
\begin{equation*}
	\sum_{i}\sum_{j} m_i m_j' = \sum_{i} m_i \sum_{j} m_j' = d_A^2 d_B^2,
\end{equation*}
where $d_A, d_B$ are the dimensions of $\rho_A, \rho_B$ respectively, and
so the set $\{(w_i w_j', m_i m_j')\}$ contains exactly the Wigner components of $\W{\rho_A \otimes \rho_B}(\x_A \oplus \x_B)$.
\end{proof}
The above result also applies when we consider re-scaled Wigner distributions, crucially due to the multiplicativity result shown in~\cref{prop:rescaled_multi}.

In the case of distillation protocols, we are interested in copies of distributions. 
For this, we have the following result, which follows from combinatorics.
\begin{lemma}\label{lem:ncopycomponents}
	Suppose $W_\rho(\x)$ has a set of $D$ component-multiplicity pairs $\{(w_i, m_i)\}$. Then, $W_{\rho^{\otimes n}} (\x)$ has component-multiplicity pairs $\{(W_{\q}, M_{\q})\}$, with index $\q$ running through all vectors $(q_1, \dots, q_D)$, where $q_1, \dots, q_D$ are non-negative integers that sum to $n$, and
\begin{align}
	W_{\q} &= \prod_{i=1}^D w_i^{q_i} \label{eq:W}\\
	M_{\q} &= \binom{n}{q_1,q_2, \dots, q_d} \prod_{i=1}^D m_i^{q_i}. \label{eq:M}
\end{align}
The term outside the product in the expression for $M_{\q}$ is the generalized binomial coefficient,
\begin{equation}
	\binom{n}{q_1,q_2, \dots, q_d} := \frac{n!}{q_1!\dots q_D!}.
\end{equation}
\end{lemma}
\begin{proof}
	Denote by $C_D^n \coloneqq \{\bmk\}$ the set of all vectors $\bmk \coloneqq (k_1, \dots, k_D)$ with non-negative integer components that sum to $n$, i.e.
	\begin{equation*}
	0 \leq k_1, \dots, k_D \leq n \text{ and } k_1 + \dots + k_D = n.
	\end{equation*}

	We proceed by induction.	
	Assume $n = 1$ and let $\bmk_i$ be the vector with its $i$-th component equal to 1 and 0's elsewhere.
	The set $C_D^1$ consists of all vectors of this form, i.e. 
\begin{equation*}
	C_D^1 = \{ \bmk_i \}_{i=1,\dots,D}
\end{equation*}
	It is also true by direct calculation that
\begin{equation*}
	\left( W_{\bmk_i}, M_{\bmk_i} \right) = (w_i, m_i).
\end{equation*}
Therefore, $\{ (W_{\bmk}, M_{\bmk}) \}_{\bmk \in C_D^1}$ is a complete set of component-multiplicity pairs for $W_\rho(\x)$.

	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$--copy distribution $W_{\rho^{\otimes n}}(\bmx) = W_{\rho}(\bmx)^{\otimes n}$.
	By construction, the distribution $W_{\rho}(\bmx)^{\otimes (n+1)} = W_{\rho}(\bmx)^{\otimes n} \otimes W_{\rho}(\bmx)$, so it admits the complete set of component multiplicity pairs
\begin{equation}
	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
\end{equation}

	Consider the component sum of the distribution $W_{\rho}(\bmx)^{\otimes (n+1)}$,
\begin{align*}
	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
\end{align*}
where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
\begin{align*}
	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
\end{align*}
We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.

We have achieved a regrouping of the distribution components.
Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
\begin{align*}
	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{2(n+1)},
\end{align*}
which is the dimension of $W_{\rho}(\bmx)^{\otimes (n+1)}$.

Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ contains exactly the components of $W_{\rho}(\bmx)^{\otimes n}$, completing the proof.
\end{proof}
Once again, the above result applies on re-scaled Wigner distributions as well.

\subsection{Results on Lorenz curve constraints}
\label{app:lc_constraints}

We first prove the following result on the relation between majorization in a particular fragment and mana, which was stated in~\cref{sec:monotones_frag}.
\begingroup
\def\thetheorem{\ref{lem:lcmax}}
\begin{theorem}
	Given a magic state $\rho$, the maximum value $L_\star$ attained by the Lorenz curve $\lc{\rho}{\sigma}(x)$ is independent of the $\sigma$--fragment and equal to $1+\sn{\rho}$. Moreover, the relative majorization constraint is stronger than mana in every fragment.
\end{theorem}
\addtocounter{theorem}{-1}
\endgroup
\begin{proof}
	We denote the Wigner distributions of the states single-component vectors $\w(\rho)=W_\rho(x)$ and $ \w(\sigma)=W_\sigma(x)$. Likewise, we write $\w(\rho|\sigma) = W_{\rho|\tau}(\x)$.
	We choose the component indexing so that $\w(\rho|\sigma)^\downarrow = \w(\rho|\sigma)$ and so the components are sorted in non-increasing order.
